Practical Optional Types for Clojure

### 2016-01-07 overview.tex
nil restrictions

Typed Clojure rejects programs that assume methods cannot return \clj{nil}.
%
\begin{minted}{clj}
(defn parent-bad-out [f :- File] :- Str
  (.getParent f)) ; Type Error: Expected Str, given (U nil Str).
\end{minted}
Since Java-level types lack nullability information,
Typed Clojure conservatively assumes Java methods and
constructor arguments cannot be passed \clj{nil}---this restriction can be
adjusted per method, but method targets can never be \clj{nil}.

>>>>

Typed Clojure rejects programs that assume methods cannot return \clj{nil}.
%
\begin{minted}{clj}
(defn parent-bad-out [f :- File] :- Str
  (.getParent f)) ; Type Error: Expected Str, given (U nil Str).
\end{minted}
Method targets can never be \clj{nil}.
Typed Clojure also prevents passing \clj{nil} as Java method or
constructor arguments by default---this restriction can be
adjusted per method.
